---
title: "R workshop draft"
author: "keyla"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    fig_width: 10
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load}
data<-read.csv("FFB.Keyla.Group.csv")
library(ggplot2)
library(reshape2)
library(tidyverse)
library(dplyr)

names(data)[names(data) == "Condition...1..Unfamiliar.country.eats.familiar.food..2..unfamiliar.country.eats.unfamiliar.food.."] <- "unfamCountryfoodpair"

names(data)[names(data) =="Rating...1.Really.don.t.like..to.4.Really.like."]<-"ratings"

names(data)[names(data) =="Time...0..pre.test..1..post.test"]<-"prePosttest"

names(data)[names(data) =="PID...Participant.ID..4.lines.per.participants"]<-"pid"

names(data)[names(data) =="FoodFam...Which.type.of.food.children.saw.them.with..0..unfamiliar..1..familiar"]<-"FamUnfamFood"
data$GroupCountryFam<-as.factor(data$GroupCountryFam)
data$unfamCountryfoodpair<-as.factor(data$unfamCountryfoodpair)
data$prePosttest<-as.factor(data$prePosttest)
data$FamUnfamFood<-as.factor(data$FamUnfamFood)
```
## Overview

This report presents preliminary data analysis from a study conducted by the UCSB child Studies Lab. Basically this will report basic descriptive statistics as well as report tests of the following predictions:

1. Children will like people from America more than from Suriname
2. Children will like people who eat familiar foods more than people who eat unfamiliar foods
3. Liking will increase after learning that people eat familiar foods
  



```{r dataprep}
preference_table <- table(data$GroupCountryFam, data$ratings)
preference_table
```

## Prediction 1 Analysis

We can reject the null hypothesis, indicating that there is a significant association between country familiarity and general likability. In other words children liked kids from America more than kids from Suriname. 

```{r p1}
#run one-way anova
p1 <-aov(ratings~GroupCountryFam+Error(pid),data=data)
#output result
summary(p1)

plot1 <- ggplot(data = data,
                  aes(x = GroupCountryFam,
                      y = ratings,
                      fill =GroupCountryFam)) +
  labs(x = "Country", y = "Likability Rating") +
  scale_x_discrete(labels = c("Suriname","America" )) +
 
  theme_grey(base_size = 20) +
  guides(fill=F)+
  geom_violin(position=position_dodge(.9))+
  geom_boxplot(position=position_dodge(.9),
               width=.1)
plot1
```


## Prediction 2 Analysis
significant change, children like people who eat familiar foods more than unfamiliar foods. 

```{r p2}
# anova
p2<-aov(ratings~FamUnfamFood+Error(pid),data = data)
summary(p2)

#Graph it
plot2 <- ggplot(data = data,
                  aes(x = FamUnfamFood,
                      y = ratings,
                      fill =FamUnfamFood)) +
  labs(x = "Food Familiarity", y = "Likability Rating") +
  scale_x_discrete(labels = c("Unfamiliar Food","Familiar Food" )) +
 
  theme_grey(base_size = 20) +
  guides(fill=F)+
  geom_violin(position=position_dodge(.9))+
  geom_boxplot(position=position_dodge(.9),
               width=.1)
plot2

```

### Prediction 2.2
```{r p2.2}
p2.2<-aov(ratings~FamUnfamFood+Error(pid),data = data[data$GroupCountryFam==0,])
summary(p2.2)

#Graph it
plot2.2 <- ggplot(data = data[data$GroupCountryFam==0,],
                  aes(x = FamUnfamFood,
                      y = ratings,
                      fill =FamUnfamFood)) +
  labs(x = "Food Familiarity", y = "Likability Rating (Suriname Only") +
  scale_x_discrete(labels = c("Unfamiliar Food","Familiar Food" )) +
 
  theme_grey(base_size = 20) +
  guides(fill=F)+
  geom_violin(position=position_dodge(.9))+
  geom_boxplot(position=position_dodge(.9),
               width=.1)
plot2.2

```


## Prediction 3 Analysis

We fail to reject the null hypothesis, meaning that there was no significant change in the Pre to Post test ratings after the unfamiliar country was paired with either a familiar or unfamiliar food.This indicates that children opinions don't seem to change after learning that people eat familiar foods.

```{r p3}
p3<-aov(ratings~prePosttest*FamUnfamFood+Error(pid),data=data)
summary(p3)

#graph it
plot3 <- ggplot(data = data,
                  aes(x = FamUnfamFood,
                      y = ratings,
                      fill =prePosttest)) +
  labs(x = "Food Familiarity", y = "Likability Rating",fill="Pre/Post Test") +
  scale_x_discrete(labels = c("Unfamiliar Food","Familiar Food" )) +
   scale_fill_manual(values=c("deeppink4","skyblue"),
                    labels=c("Pre-Test","Post-Test"))+
 
  theme_grey(base_size = 20) +
  geom_violin(position=position_dodge(.9))+
  geom_boxplot(position=position_dodge(.9),
               width=.1)
plot3
```
####
by country
```{r}
plot3.2 <- ggplot(data = data,
                  aes(x = FamUnfamFood,
                      y = ratings,
                      fill =prePosttest)) +
  labs(x = "Food Familiarity", y = "Likability Rating",fill="Pre/Post Test") +
  scale_x_discrete(labels = c("Unfamiliar Food","Familiar Food" )) +
   scale_fill_manual(values=c("deeppink4","skyblue"),
                    labels=c("Pre-Test","Post-Test"))+
 
  theme_grey(base_size = 20) +
  geom_violin(position=position_dodge(.9))+
  geom_boxplot(position=position_dodge(.9),
               width=.1)+
  facet_wrap(~factor(GroupCountryFam,labels=c("Suriname","America")))
plot3.2

ggsave("plot3.2.tiff",plot3.2,width=10,height=6,units="in",dpi=150)
```


